draft_final_assignment

### 2022-11-28 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

```{r }
df <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/data_11_28.csv")
```
## Creating a corpus
```{r }
df_corp <- df
df_corp <- df_corp %>% rename(text = summary)
corp <- corpus(df_corp)
```

@@

```{r }
dfmat_115 <- dfm(corpus_subset(corp, session == 115), remove = stopwords("english"), remove_punct = TRUE,
                remove_numbers = TRUE) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
    dfm_trim(min_termfreq = 1)

@@

dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Party) %>%
    dfm_trim(min_termfreq = 3)

textplot_wordcloud(dfmatRepDem, comparison = TRUE, max_words = 300,
                   color = c("blue", "red"))

@@

#Wordcloud comparing Congresses
```{r }
dfmatCon <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Congress) %>%
    dfm_trim(min_termfreq = 3)

>>>>

```{r }
df <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/data_11_28.csv")
```

## Creating party variable
```{r }
df$party <- ifelse(df$cosponsor_D_perc > 0.66, "Democrat", ifelse(df$cosponsor_R_perc > 0.66, "Republican", "Both"))
```

## Creating a corpus
```{r }
df_corp <- df
df_corp <- df_corp %>% rename(text = summary)
corp <- corpus(df_corp)
```

@@

```{r }
dfmat_115 <- dfm(corpus_subset(corp, session == 115), remove = stopwords("english"), remove_punct = TRUE,
                remove_numbers = TRUE) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
    dfm_trim(min_termfreq = 3)

@@

dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$party) %>%
    dfm_trim(min_termfreq = 3)

textplot_wordcloud(dfmatRepDem, comparison = TRUE, max_words = 300,
                   color = c("green","blue", "red"))

@@

#Wordcloud congress parties 115

```{r }

corp_115 <- df %>% filter(session == 115) %>% rename(text = summary) %>% corpus()
modelpart15 <- dfm(corp_115, remove = stopwords("english"), remove_punct = TRUE, groups = corp_115$party) %>% dfm_trim(min_termfreq = 3)

mp15 <- textplot_wordcloud(modelpart15, comparison = TRUE, max_words = 300,
                   color = c("green","blue", "red"))
mp15

#Wordcloud congress parties 116

```{r }

corp_116 <- df %>% filter(session == 116) %>% rename(text = summary) %>% corpus()
modelpart16 <- dfm(corp_116, remove = stopwords("english"), remove_punct = TRUE, groups = corp_116$party) %>% dfm_trim(min_termfreq = 3)

mp16 <- textplot_wordcloud(modelpart16, comparison = TRUE, max_words = 300,
                   color = c("green","blue", "red"))
mp16

#Wordcloud congress parties 117

```{r }

corp_117 <- df %>% filter(session == 117) %>% rename(text = summary) %>% corpus()
modelpart17 <- dfm(corp_117, remove = stopwords("english"), remove_punct = TRUE, groups = corp_117$party) %>% dfm_trim(min_termfreq = 3)

mp17 <- textplot_wordcloud(modelpart17, comparison = TRUE, max_words = 300,
                   color = c("green","blue", "red"))

mp17

#Wordcloud comparing Congresses
```{r }
dfmatCon <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$session) %>%
    dfm_trim(min_termfreq = 3)
